---
title: "Examining the performance of DA Bulgaria in the 2017 Parliamentary elections outside Bulgaria"
output: html_notebook
---

Data source: https://results.cik.bg/pi2017/csv.html 

Data analysis: Vesela Grozeva

Objective: Examine which locations favored "DA Bulgaria." 

# Aggregate performance in sections abroad, excluding Turkey


```{r}
load("ballots_agg")
kable(ballots_agg, format.args = list(big.mark = ","), align="c", col.names=c("Valid votes", "Votes per party", "Party No", "Party Name", "Percentage of valid votes")) 

```

```{r}
ggplot(data=ballots_agg, aes(y=agg_votes_perc, x=reorder(party_names, -agg_votes_perc))) + geom_bar(stat="identity") + 
            theme_minimal() + 
            theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
            labs(title="Composition of Bulgaria's foreign vote, outside of Turkey", x="Party", y="Percent of valid votes cast")
```

"DA Bulgaria" gathered 13.8% of the total vote outside Bulgaria (excluding Turkey) and was 3rd after GERB and BSP.

# "DA Bulgaria" performance by country

Which countries garnered the most support for "DA Bulgaria"? Variable "votes_perc_bycountry" indicates the percent of valid votes cast for 
"DA Bulgaria" by country. 

```{r}
load("ballots_country")
ballots_country <- filter(ballots_country, party_id=="P16")
column_names <- c("Country", "Party No", "Party Name", "Total votes", "Valid votes", "Votes per party", "Percentage of valid votes" )
kable(ballots_country[order(-ballots_country$votes_perc_bycountry), ], align="c", col.names=column_names)
```

```{r}
ggplot(data=ballots_country, aes(y=votes_perc_bycountry, x=reorder(country, -votes_perc_bycountry))) + geom_bar(stat="identity") + 
            theme_minimal() + 
            theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
            labs(title="Percent of the vote earned by DA Bulgaria by country", x="Party", y="Percent of valid votes cast")
```

# "DA Bulgaria" performance by city

Which cities garnered the most support for "DA Bulgaria"? Variable "votes_perc_bycity" indicates the percent of valid votes cast for 
"DA Bulgaria" by country. 

```{r}
load("ballots_city2")
ballots_city <- filter(ballots_city2, party_id=="P16")
column_names <- c("City", "Country", "Party No", "Party Name", "Total votes", "Valid votes", "Votes per party", "Percentage of valid votes" ) 
kable(ballots_city[order(-ballots_city$votes_perc_bycity), ], align="c", col.names = column_names) 
```


```{r}
ballots_city_first50 <- ballots_city[order(-ballots_city$votes_perc_bycity), ][c(1:50) , ]
ggplot(data=ballots_city_first50, aes(y=votes_perc_bycity, x=reorder(city, -votes_perc_bycity))) + geom_bar(stat="identity") + 
            theme_minimal() + 
            theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
            labs(title="DA Bulgaria by city for the 50 cities with highest support", x="Party", y="Percent of valid votes cast")
```


```{r}
ballots_city_last50 <- ballots_city[order(-ballots_city$votes_perc_bycity), ][c(242:292) , ]
ggplot(data=ballots_city_last50, aes(y=votes_perc_bycity, x=reorder(city, -votes_perc_bycity))) + geom_bar(stat="identity") + 
            theme_minimal() + 
            theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
            labs(title="DA Bulgaria by city for the 50 cities with weakest support", x="Party", y="Percent of valid votes cast")
```


