---
title: "Mapping the results of the 2017 Parliamentary elections outside Bulgaria"
output: html_notebook
---

Author: Vesela Grozeva

Data source: https://results.cik.bg/pi2017/csv.html 

Data processing: https://github.com/VesGr/BGelections2017analysis 


The raw data has been processed and synthesized in a dataframe called "ballots_city." It contains results aggregated by location as certain locations have more than one voting section. Only the results for the main political parties are shown - these parties are:

* DA Bulgaria
* GERB
* BSP
* Patrioti
* Volia
* Reformatorski Bloc (RB)
* DPS
* DOST

The "total votes" variable indicates the total number of votes cast, including votes that were deemed invalid or that indicated that the voter does not support any party. 

Map use: click on map to zoom in and click on the pins to display the statistics for that location.

*Votes by count:*


```{r}
require(leaflet)
load("ballots_city") 
popup_text <- paste0("Location: ", ballots_city$locations, "<br>Total votes: ", ballots_city$tot_ballots_bycity, "<br>DA Bulgaria: ", ballots_city$P16, "<br>GERB: ", ballots_city$P11, "<br>BSP: ", ballots_city$P10, "<br>Patrioti: ", ballots_city$P17, "<br>Volia: ", ballots_city$P6, "<br>RB: ", ballots_city$P21, "<br>DPS: ", ballots_city$P9, "<br>DOST: ", ballots_city$P13)

leaflet(ballots_city) %>% addTiles() %>% addMarkers(popup=popup_text) 

```

*Votes by percentage:*


```{r}
popup_text <- paste0("Location: ", ballots_city$locations, "<br>Total votes: ", ballots_city$tot_ballots_bycity, "<br>DA Bulgaria: ", ballots_city$P16_pct, "<br>GERB: ", ballots_city$P11_pct, "<br>BSP: ", ballots_city$P10_pct, "<br>Patrioti: ", ballots_city$P17_pct, "<br>Volia: ", ballots_city$P6_pct, "<br>RB: ", ballots_city$P21_pct, "<br>DPS: ", ballots_city$P9_pct, "<br>DOST: ", ballots_city$P13_pct)

leaflet(ballots_city) %>% addTiles() %>% addMarkers(popup=popup_text) 
```






